Treebeard : An Optimizing Compiler for Tree Based ML Inference

### 2022-04-16 docs/MICRO 2022/overview.tex
Edit figure captions

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figures/compiler.pdf}
  \caption{Treebeard Compiler Structure}
  \label{Fig:CompilerStructure}
\end{figure}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{figures/OverviewExample.pdf}
  \caption{Treebeard IR lowering and optimization details}
  \label{Fig:Overview}
\end{figure*}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figures/compiler.pdf}
  \caption{Treebeard compiler structure}
  \label{Fig:CompilerStructure}
\end{figure}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{figures/OverviewExample.pdf}
  \caption{Treebeard IR lowering and optimization details. The three abstraction level in Treebeard's IR are shown. The
           high level IR is a tree based IR to perform model level optimization, the mid-level IR is for
           loop optimizations that are independent of memory layout and the low level IR allows us to perform
           vectorization and other memory layout dependent optimizations.}
  \label{Fig:Overview}
\end{figure*}
